Case Study (Hannah)

### 2020-05-06 Code/MRP-Hannah/Case Study (Hannah).Rmd
updates citations

---
title: "Case Study (McKenna)"
author: "McKenna Weech"
date: "3/10/2020"
output: html_document
---

@@

```{r message = FALSE}
library(tidyverse) #Load packages
library(rstan)
library(rstanarm)
library(ggplot2)
library(bayesplot)
theme_set(bayesplot::theme_default())
library(dplyr)
library(tidyr)
library(tidybayes)
library(here)

@@

For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model. The function will also generate an MRP table to use later to poststratify.

@@

We include the function here just for reference. The outputs have been previously saved out as "sample", "postrat", and "true_popn".

```{r, eval = FALSE}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

@@

Here we will import our data generated by the function.

@@

sample <- read_csv(here:here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here:here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here:here("code", "mrp", "data", "true_popn.csv"))

```
We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model

In this section we are working througha couple different model versions heading to the hierarichal model.

Here we are looking at running a simple logit model.

@@

```{r}
fit <- stan(
  file = here::here("Code", "mrp", "logit_simple.stan"),
  data = stan_data,
  seed = 42
)

```
```{r, eval = FALSE}
fit %>%
  mcmc_trace(
    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
    n_warmup = 500,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
```

Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working. 
```{r}
 matrix <- sample %>% 
  select(male, age, eth, income, state)

x <- as.matrix(matrix)
```

This is me thinking about what format we want the data in.

```{r}
stan_data <- list(
  N = 1200,                                       # Number of observations.
  K = 6300,                                       # Number of groups.
  g = sample(6300, 1200, replace = TRUE),         # Vector of group assignments

@@

Here we are trying to do a higherarical logit.

```{r}
data_list <- list(
  D <- 5,                                    # Number of variables. 
  N <- 1200,                                 # Number of observations.
  L <- 6300,                                 # Number of groups. 
  y <- sample$service_failure,               # Outcome variables. 
  ll <- sample(6300, 1200, replace = TRUE),  # Group assignment. 
  x <- as.matrix(matrix)                     # Matrix of predictors. 
)
```

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42
)
```

>>>>

---
title: "Case Study (Hannah)"
author: "Hannah Thompson"
date: "3/10/2020"
output: html_document
---

@@

```{r message = FALSE}
library(tidyverse) #Load packages
library(rstan)
library(rstanarm)
library(ggplot2)
library(bayesplot)
theme_set(bayesplot::theme_default())
library(dplyr)
library(tidyr)
library(tidybayes)

@@

For this first iteration of modeling, we will be generating our own data. We will generate a population, and sample from it in order to build an MRP model.

@@

```{r}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

@@

@@

mrp_sim <- simulate_mrp_data(n=1200)

sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]

head(sample)

```
```{r}
sample <- read_csv(here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here("code", "mrp", "data", "true_popn.csv"))
```

@@

```{r}
fit <- stan(
  file = here::here("Code", "mrp", "logit_simple.stan"),
  data = stan_data,
  seed = 42
)
```

```{r}
fit %>%
  mcmc_trace(
    pars = c("alpha","beta1", "beta2", "beta3", "beta4"),
    n_warmup = 5,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
```
```{r}

We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model

sim_values <- list(
  N = 6300,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

  male = sample(2, 6300, replace = TRUE),            # Vector of group assignments.
  eth = sample(3, 6300, replace = TRUE),       # Vector of brands covariates.
  age = sample(7, 6300, replace = TRUE),        # Vector of price covariates.
  income = sample(3, 6300, replace = TRUE),
  state = sample(50, 6300, replace = TRUE),

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code", "mrp", "generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)

# Extract the simulated data.
prior_pc <- tibble(
  service_failure = as.vector(extract(sim_data)$service_failure)
)
# Plot the prior predictive distribution.
prior_pc %>% 
  ggplot(aes(x = service_failure)) +
  geom_density()

Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.

```{r}
stan_values <- list(
  N = 1200,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

@@

```{r}
fit3 <- stan(
  file = here::here("Code", "mrp", "logit_simple.stan"),
  data = stan_values,
  seed = 42
)
```
